---
title: "Irene Data Analysis Progress"
author: "Mwaura Patrick"
date: "2/8/2021"
output: word_document
editor_options: 
  chunk_output_type: inline
---

```{r setupr ,echo=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm()
library(xml2)
library(rvest)
library(curl)
library(testthat)
library(pillar)
library(clipr)
library(officer)
library(rmarkdown)
library(conflicted)
library(tidyr)
library(tidyverse)
library(dplyr)
conflict_prefer("filter", "dplyr")
conflict_prefer("mutate", "dplyr")
library(readxl)
library(here)
library(plyr)
conflict_prefer("summarize", "plyr")
conflict_prefer("summarise", "dplyr")
library(skimr)
library(kableExtra)
library(AMR)
library(scales)
library(pipeR)
library(cleaner)
library(htmlTable)
library(data.table)
library(janitor)
library(reshape)
library(reshape2)
conflict_prefer("melt", "reshape2")
library(summarytools)
conflict_prefer("freq", "cleaner")
library(magrittr)
library(epiDisplay)
conflict_prefer("select", "dplyr")
conflict_prefer("view", "tibble")
library(vcdExtra)
library(formattable)
library(gt)
conflict_prefer("chisq.test", "janitor")
library(flextable)
library(huxtable)
conflict_prefer("rename", "dplyr")
conflict_prefer("fmt_percent","huxtable")
setwd("E:/RESULTS/Mwaura/mwaura/WORK1/Covid19/Irene Work")
IRENE_DATA_ANALYSIS_R <- fread("IRENE DATA ANALYSIS R.csv")
```


## Summary of the data

View the summary of the data
```{r r setupr ,echo=FALSE,message=FALSE}
#skimr::skim(IRENE_DATA_ANALYSIS_R) %>% flextable() 
#glimpse(IRENE_DATA_ANALYSIS_R)

```


## Number of camels from each of the Livestock Production System 
With their Percentages and Bar Graph

H0: There is no association/relationship between community/ranch and the livestock production system
H1: There is an association / relationship between community/ranch and livestock production system


Reject the null hypothesis
```{r, echo=FALSE}
comm<-IRENE_DATA_ANALYSIS_R %>% tabyl(Community,LPS) 

comm %>% adorn_totals(c("row","col")) %>%adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 0) %>%
  adorn_ns() %>% flextable()%>% theme_zebra() %>% border(border=fp_border(color = "black"),part = "all") %>% add_header_lines(values="Ranch vs Livestock production system With Percentages") %>% fontsize(i=1,size=14,part="header")

comm%>%chisq.test() 
janitor::fisher.test(comm)

#IRENE_DATA_ANALYSIS_R %>% select(Community,LPS) %>%  ggplot(aes(x=Community,fill=LPS))+geom_bar(color="blue",fill="blue")+ylab("Number of Camels")+stat_count(geom="text",aes(label=stat(count)), position = position_stack(vjust = .9),color="white")

IRENE_DATA_ANALYSIS_R %>% select(Community,LPS) %>%  ggplot(aes(x=Community,fill=LPS))+geom_bar()+ylab("Number of Camels")+stat_count(geom="text",aes(label=stat(count)), position = position_stack(vjust = .9),color="black")

```



## Counts and Percentages of E.coli Isolated from all the camels
This table counts and percentages of E.coli isolates in Extensive/Intensive location/Livestock procuction system

H0: There is no association/relationship between micro organism and the livestock production system
H1: There is an association / relationship between micro organism and livestock production system


Reject the null hypothesis



```{r,echo=FALSE}
mo<-IRENE_DATA_ANALYSIS_R %>% tabyl(mo,LPS) 

mo %>% adorn_totals(c("row","col")) %>%  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 0) %>%
  adorn_ns() %>%  flextable()%>% theme_zebra() %>% border(border=fp_border(color = "black"),part = "all")%>% border(part = "all")%>% add_header_lines(values="E.coli recovered from each of the LPS") %>% fontsize(i=1,size=14,part="header") 

mo%>%chisq.test() 
janitor::fisher.test(mo)
```



## Pie Chart
The above table can be visualised as a pie chart
```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% select(mo,CAMEL_ID_NUMBER) %>% group_by(mo) %>%  dplyr::summarise(n = n()) %>% mutate(Percentage=paste0(round(n/sum(n)*100,0),"%")) %>% ggplot(aes(x="", y=mo, fill=Percentage)) + geom_bar(stat="identity", width=1)+ coord_polar("y" ,start=0) +theme_classic()+labs( title = "Percentage of E.coli  Detected")+scale_fill_manual(values=c( "#33658A", "#F6AE2D"))+theme(axis.line = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(), plot.title = element_text(hjust = 0.5, color = "black"))+geom_text(aes(y = mo,label="E.coli"), position = position_stack(vjust = .5),color = "#F6AE2D", size=4)
```

## Counts and percentages of the number of camels (female and male) from each livestock production system

H0: There is no association/relationship between gender and the livestock production system
H1: There is an association / relationship between gender and livestock production system

Reject the Null hypothesis:There is a significant relationship between Gender and Livestock production system. Therefore, knowing the value of one  may help to give vital information about the other
.
```{r,echo=FALSE}
tab<-IRENE_DATA_ANALYSIS_R %>% tabyl(Gender,LPS)  
tab %>% adorn_totals(c("row","col"))%>%  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 0) %>%
  adorn_ns()  %>% flextable()%>% theme_zebra() %>% border(border=fp_border(color = "black"),part = "all")%>% border(part = "all") %>% add_header_lines(values="Camels(Female and Male) from each of the LPS") %>% fontsize(i=1,size=14,part="header")


IRENE_DATA_ANALYSIS_R %>% tabyl(Gender,LPS)%>%chisq.test() 
IRENE_DATA_ANALYSIS_R %>% tabyl(Gender,LPS) %>% janitor::fisher.test()

```


## The count and percentages of  Resistance/Intermediate/Susceptible E.coli to all the antibiotics

```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% count_df(translate_ab = TRUE,combine_SI = FALSE) %>% spread(key = interpretation,value = value) %>% adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 0)%>%
    adorn_ns()%>% flextable()%>% theme_zebra() %>% border(border=fp_border(color = "black"),part = "all")%>% add_header_lines(values="Antibiotic Susceptibility  Intermediate and Resistance") %>% fontsize(i=1,size=14,part="header")
```

## Bug Drug Combination and grouping where possible

```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R%>% select(mo,AMC:NOR) %>% filter(mo=="Escherichia coli") %>% mutate_at(vars(AMC:NOR), as.rsi) %>% bug_drug_combinations(FUN = mo_gramstain) %>% format(col_mo=NULL,language=get_locale(),translate_ab="name(ab,atc)",add_ab_group=TRUE) %>% flextable()%>% theme_zebra() %>% border(border=fp_border(color = "black"),part = "all")%>% add_header_lines(values="Antibiotics Combination") %>% fontsize(i=1,size=14,part="header")
                                                                                                                    
                                                                                              
```


## Beta-lactams/Penicillins
Beta-lactam antibiotics are one of the most commonly prescribed drug classes with numerous clinical indications.

From a biochemical point of view, these drugs have a common feature, which is the 3-carbon and 1-nitrogen ring (beta-lactam ring) that is highly reactive. This class includes:

Penicillins,Cephalosporins,Carbapenems,Monobactams,Beta-lactamase inhibitors

column 'AMC' (amoxicillin/clavulanic acid), column 'AMP'
                                    (ampicillin), column 'OXA' (oxacillin), column 'TEM' (temocillin)
NOTE: No antimicrobial agents of class cephalosporins (1st gen.) found (such as cefacetrile,
      cephapirin).
      Selecting cephalosporins (2nd gen.): column 'CEC' (cefaclor), column 'CXM' (cefuroxime)
NOTE: No antimicrobial agents of class carbapenems found (such as doripenem, imipenem).
```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(AMP,AMP,CEC,FEP,CXM,CRO,CTX,CAZ)%>% mutate_at(vars(AMP:CAZ), as.rsi) %>% count_df(translate_ab = TRUE,combine_SI = FALSE) %>% spread(key =interpretation,value = value ) %>% adorn_percentages("row") %>%
    adorn_pct_formatting(digits = 0) %>%
    adorn_ns() %>%  flextable()%>% theme_zebra() %>% border(border=fp_border(color = "black"),part = "all")%>% add_header_lines(values="Beta-lactams Antibiotic Susceptibility Intermediate and Resistance") %>% fontsize(i=1,size=14,part="header")

```


## Resistance

```{r,echo=FALSE, warning=FALSE}

#theme_set(
  #theme_minimal() +
  #  theme(legend.position = "right")
 # )

#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo)%>%filter(mo=="Escherichia coli") %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),SXT=resistance(SXT),NOR = resistance(NOR)) %>% tidyr::pivot_longer(-mo, names_to = "antibiotic") %>% huxtable() %>% set_number_format(row=1:16,col="value",fmt_percent(2)) %>%huxtable::as_flextable()%>% theme_vanilla() %>% border%>% add_header_lines(values="E.coli Percentate resistance to individual Antibiotics")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo)%>%filter(mo=="Escherichia coli") %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),SXT=resistance(SXT),NOR = resistance(NOR)) %>% tidyr::pivot_longer(-mo, names_to = "antibiotic") %>% ggplot(aes(x = mo,y = value,fill = antibiotic)) +geom_col(position = "dodge2")#+ scale_fill_grey(start = 0, end = 0.5) 

#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo)%>%filter(mo=="Escherichia coli") %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),SXT=resistance(SXT),NOR = resistance(NOR)) %>% tidyr::pivot_longer(-mo, names_to = "antibiotic") %>% gt() %>% gt::fmt_percent(columns = 3,decimals = 2) %>% write.csv("E:/RESULTS/Mwaura/mwaura/WORK1/Covid19/Irene Work\\Resistance.csv", row.names = FALSE)
#Resistance<-read.csv("Resistance.csv")
#Resistance %>% ggplot(aes(x = mo,y = Percentage,fill = Antibiotics)) +geom_col(position = "dodge2")#+ scale_fill_grey(start = 0, end = 0.5) 

#IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% ggplot_rsi(position= "dodge",datalabels=FALSE,x.title="Antimicrobial",y.title="Proportion",colours=c(S="#61a8ff",R="#ff6961",I="black"),combine_SI=FALSE,translate_ab=FALSE,title="Relative comparison of Resistance against Susceptability and Intermediate combined")+geom_rsi(translate_ab = FALSE) + scale_y_percent(breaks = 0:4*25)+theme_rsi()+labels_rsi_count(position = NULL,translate_ab = FALSE,datalabels.size = 3,datalabels.colour = "black")+coord_flip()+labs(subtitle = "N=123")

IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% ggplot_rsi(translate_ab=FALSE,combine_SI = FALSE,combine_IR = FALSE,title = "Plot for R,S and I",caption = "To get the percentages, please consider the tables provided")+geom_rsi(translate_ab = FALSE,combine_SI = FALSE) + scale_y_percent(breaks = 0:4*25)+theme_rsi()+labels_rsi_count(position = NULL,translate_ab = FALSE,combine_SI = FALSE,    datalabels.colour = "black")+coord_flip(expand = TRUE)+labs(subtitle = "n=123")+theme(legend.position = "bottom")

```



## Comparison table(extensive and Intensive)- percentage , resistance to all antibiotics

```{r echo=FALSE, warning=FALSE}
#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% proportion_df(combine_SI = FALSE) %>% spread(key = interpretation,value = value) %>% kbl(caption = "Antibiotic Susceptability Intermediate and Resistance") %>%  kable_classic(full_width = F, html_font = "Cambria")


#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,combine_SI = FALSE) %>% spread(key = antibiotic,value = value) %>% unnest()%>% kbl(caption = "Comparision of Livestock Production system with their resistant to all antibiotics") %>%  kable_classic(full_width = F, html_font = "Cambria")

#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,as_percent=FALSE,combine_SI = TRUE) %>% spread(key = antibiotic,value = value) %>% unnest()%>%  adorn_percentages("row") %>% adorn_pct_formatting(digits = 0)%>% kbl(caption = "Comparision of Livestock Production system with their resistant to all antibiotics") %>%  kable_classic(full_width = F, html_font = "Cambria")

#anti<-IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,combine_SI = FALSE,as_percent = FALSE) %>% spread(key = antibiotic,value = value) %>% melt(id.vars=c("LPS","interpretation"),measure.vars=c("AMC","AMP","CAZ","CEC","CHL","CIP","CRO","CTX","CXM","FEP","GEN","NOR","SPT","SXT","TCY"))

#struct<-IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,combine_SI = FALSE)  %>% spread(key = antibiotic,value = value) %>% melt(id.vars=c("LPS","interpretation"),measure.vars=c("AMC","AMP","CAZ","CEC","CHL","CIP","CRO","CTX","CXM","FEP","GEN","NOR","SPT","SXT","TCY")) %>% gt() %>% gt::fmt_percent(columns = 4,decimals = 2)

#write.csv(struct,"E:/RESULTS/Mwaura/mwaura/WORK1/Covid19/Irene Work\\struct.csv", row.names = FALSE)

#struct<-xtabs(value~LPS+interpretation+variable,data =struct )

#struct %>% as.data.table() %>% dplyr::arrange(LPS) %>% spread(key = interpretation,value = value) %>% as_grouped_data(groups = c("LPS")) %>% flextable::as_flextable()  %>% theme_vanilla() %>% border%>% add_header_lines(values="Comparison table(Extensive and Intensive) Percentages , Resistance to all antibiotics")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header") 
#LPS<-structable(struct)
#LPS
struct<-read.csv("struct.csv")

lps<-struct %>% as.data.table() %>% dplyr::arrange(LPS) %>% spread(key = interpretation,value = value)

Ext<-lps[1:15,] %>% select(-Group)  %>% as_grouped_data(groups = c("LPS"))  
colnames(Ext) <- c("LPS_Ext","AB","I.Ext","R.Ext","S.Ext")
Ext1<-Ext %>% select("AB","I.Ext","R.Ext","S.Ext") %>% na.omit()


GP<-lps[1:15,2]
colnames(GP)<-c("AB_Group")


Int<-lps[16:30,]%>% select(-Group)%>%  as_grouped_data(groups = c("LPS"))
colnames(Int) <- c("LPS_Int","A.Int","I.Int","R.Int","S.Int") 
Int1<-Int %>% select(I.Int,R.Int,S.Int) %>% na.omit()

cbind(GP,Ext1,Int1) %>%  huxtable() %>% huxtable::as_flextable() %>% merge_v(j="AB_Group")%>% theme_zebra() %>% border %>% add_header_lines(values="Comparison table(Extensive and Intensive) Percentages , Resistance to all antibiotics")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header") 



```
## Multidrug Resistance Organisms MDR

#### Please explain the two tables and what the difference mean to the study.
The main varaition is the minimal required percentage of the antimicrobial classes that must be available per isolate , rounded down . For example , at 50%, how many antibmicrobial classes must be available and hence the graphs i have presented are at 0% and 100% respectively , please guide on this and what percentage I should input.


#### Please also be aware i am following MDRO guidline as perthe publication by Magiorakos et al.

Negative	(Resistant to atmost tow(2) antibiotic)
Multi-drug-resistant (MDR)
Extensively drug-resistant (XDR)	
Pandrug-resistant (PDR)	

```{r, warning=FALSE,echo=FALSE}
#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro()%>% freq() %>%  kbl(caption = "Multdrug Resistance Organisms MDR") %>%  kable_classic(full_width = F, html_font = "Cambria")
IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro(verbose = FALSE,only_rsi_columns=TRUE,pct_required_classes = 0.0,info = interactive(),combine_SI = TRUE,col_mo = NULL)%>% tab1( col=c("green","blue"),cum.percent = FALSE,main ="Multidrug Resistance bar graph",cex.names = 0.7,cex=0.6,cex.main=1,cex.axis=0.8,horiz = TRUE,cex.lab=0.7 ) 

#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro(verbose = FALSE,only_rsi_columns=FALSE,pct_required_classes = 1,info = interactive(),combine_SI = TRUE,col_mo = NULL)%>% tab1( col=c("green","blue"),cum.percent = FALSE,main ="Multidrug Resistance bar graph",cex.names = 0.7,cex=0.6,cex.main=1,cex.axis=0.8,cex.lab=0.7 )

#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro() %>% freq() %>% select(item,count,percent) %>% huxtable()%>% set_number_format(row=1:3,col="percent",fmt_percent(1)) %>%  huxtable::as_flextable()   %>% theme_vanilla()%>% theme_vanilla() %>% border(border=fp_border(color = "black"),part = "all")%>% add_header_lines(values="Multidrug Resistance Organisms MDR") %>% fontsize(i=1,size=14,part="header")
```


## Antibiotic Profiling

```{r ,echo=FALSE, warning=FALSE}
#par(mar=rep(2,4))
#IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(ISOLATE_ID,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi)
#IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(ISOLATE_ID,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi) %>% melt(id="ISOLATE_ID") %>% filter(value=="R") 

prof<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(ISOLATE_ID,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi) %>% melt(id="ISOLATE_ID") %>% filter(value=="R") 

Profile<-plyr:: ddply(prof, .(ISOLATE_ID), summarize,  antibiotics=paste(variable,collapse=",")) 

Profile2<-tab1(Profile$antibiotics, sort.group = "decreasing",col=c("#33658A", "#F6AE2D"), cum.percent = FALSE,main ="Profile of antibiotics",cex.names = 0.7,cex=0.5,cex.main=1,cex.axis=0.7,cex.lab=0.7 )
#write.csv(Profile2,"E:/RESULTS/Mwaura/mwaura/WORK1/Covid19/Irene Work\\profile3.csv", row.names = FALSE)

Profile3<-read.csv("profile3.csv")
Profile3 %>%flextable() %>%   theme_zebra() %>%  add_header_lines(values="Antibiotics Profiles with number of isolates Resistants ")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header") 
#prof2<-prof1 %>% summarytools::freq(prof1$antibiotics,order = "freq",cumul=FALSE,report.nas = FALSE)
```


###  GENE ProfileS
```{r ,echo=FALSE, warning=FALSE}
Tem<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(TEM,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi) %>% melt(id="TEM") %>% filter(value=="R") %>% filter(TEM!="NEG") 
Tem1<-plyr:: ddply(Tem, .(TEM), summarize,  antibiotics=paste(variable,collapse=",")) 

Tem1$antibiotics<- sapply(Tem1$antibiotics,function(x) paste(unique(unlist(str_split(x,","))), collapse = ", "))
Tem1  %>% mutate(Antibiotics_Count= map_int(antibiotics, ~ .x %>%  str_trim %>%  str_split(" ") %>%  unlist() %>% n_distinct))%>% flextable() %>% theme_zebra() %>% border%>% add_header_lines(values="TEM Genes antibiotics Resistant profile")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

#SHV<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(SHV,AMC:NOR)%>% mutate_at(vars(AMC:NOR), #as.rsi) %>% melt(id="SHV") %>%filter(SHV!="NEG")
#SHV1<-plyr:: ddply(SHV, .(SHV), summarize,  antibiotics=paste(variable,collapse=","))
#SHV1 %>% flextable() %>% theme_vanilla() %>% border%>% add_header_lines(values="SHV Genes antibiotic profile")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

CTX<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(CTX_M,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi) %>% melt(id="CTX_M") %>% filter(value=="R") %>% filter(CTX_M!="NEG") 
CTX1<-plyr:: ddply(CTX, .(CTX_M), summarize,  antibiotics=paste(variable,collapse=",")) 
CTX1$antibiotics<- sapply(CTX1$antibiotics,function(x) paste(unique(unlist(str_split(x,","))), collapse = ", "))
CTX1  %>% mutate(Antibiotics_Count= map_int(antibiotics, ~ .x %>%  str_trim %>%  str_split(" ") %>%  unlist() %>% n_distinct))%>% flextable() %>% theme_zebra %>% border%>% add_header_lines(values="CTX-M Genes antibiotics Resistant profile")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")


#MEANS
```

###  GENES WITH RESPECT TO LPS
  
H0: There is no association/relationship between gene and the livestock production system
H1: There is an association / relationship between gene and livestock production system
  
```{r ,echo=FALSE, warning=FALSE}
IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(LPS,TEM)%>% filter(TEM!="NEG")%>% filter(TEM!="") %>% tabyl(TEM,LPS) %>%adorn_percentages("col")%>%
  adorn_pct_formatting(digits = 0)%>% adorn_ns()%>% flextable() %>%  theme_zebra() %>% border%>% add_header_lines(values="TEM GENE")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(LPS,TEM)%>% filter(TEM!="NEG")%>% filter(TEM!="") %>% tabyl(TEM,LPS) %>% janitor::fisher.test()

#IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli")%>% select(LPS,SHV) %>% tabyl(LPS,SHV) %>%  flextable() %>%  theme_zebra() %>% border%>% add_header_lines(values="SHV GENE")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli")%>% select(CTX_M,LPS) %>% filter(CTX_M!="NEG") %>% filter(CTX_M!="")%>% tabyl(CTX_M,LPS) %>%adorn_percentages("col")%>% 
  adorn_pct_formatting(digits = 0) %>% adorn_ns()%>% flextable() %>%  theme_zebra() %>% border%>% add_header_lines(values="CTX-M GENE")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli")%>% select(CTX_M,LPS) %>% filter(CTX_M!="NEG") %>% filter(CTX_M!="")%>% tabyl(CTX_M,LPS)%>% janitor::fisher.test()

```

###  Beta-lactams to all genes and counts pecentages

```{r ,echo=FALSE, warning=FALSE}
BG<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(TEM,AMP,AMP,CEC,FEP,CXM,CRO,CTX,CAZ)%>% mutate_at(vars(AMP,AMP,CEC,FEP,CXM,CRO,CTX,CAZ), as.rsi) %>% melt(id="TEM") %>%filter(TEM!="NEG") %>% filter(TEM!="")%>% filter(value=="R")%>%  dplyr::arrange(desc(TEM))


BG1<-plyr:: ddply(BG, .(TEM), summarize,  variable=paste(variable,collapse=","))

BG1$variable<- sapply(BG1$variable,function(x) paste(unique(unlist(str_split(x,","))), collapse = ", "))


BG1  %>% mutate(Antibiotics_Count= map_int(variable, ~ .x %>%  str_trim %>%  str_split(" ") %>%  unlist() %>% n_distinct))%>% flextable() %>%  theme_zebra() %>% border%>% add_header_lines(values="Beta-Lactams TEM GENE Resistant profile")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")


BGC<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(CTX_M,AMP,AMP,CEC,FEP,CXM,CRO,CTX,CAZ)%>% mutate_at(vars(AMP,AMP,CEC,FEP,CXM,CRO,CTX,CAZ), as.rsi) %>% melt(id="CTX_M") %>%filter(CTX_M!="NEG") %>% filter(CTX_M!="")%>% filter(value=="R")%>%  dplyr::arrange(desc(CTX_M))


BGC1<-plyr:: ddply(BGC, .(CTX_M), summarize,  variable=paste(variable,collapse=","))

BGC1$variable<- sapply(BGC1$variable,function(x) paste(unique(unlist(str_split(x,","))), collapse = ", "))


BGC1  %>% mutate(Antibiotics_Count= map_int(variable, ~ .x %>%  str_trim %>%  str_split(" ") %>%  unlist() %>% n_distinct))%>% flextable() %>%  theme_zebra() %>% border%>% add_header_lines(values="Beta-Lactams CTX-M GENE Resistant profile")%>% border(border=fp_border(color = "black"),part = "all") %>% fontsize(i=1,size=14,part="header")

```


