---
title: "Irene"
author: "Mwaura Patrick"
date: "2/8/2021"
output: word_document
---
### Irene Data Analysis

This analysis is being done at the request of the researcher

```{r ,echo=FALSE,message=FALSE}
rm()
options( warn = -1 )
library(xml2)
library(rvest)
library(curl)
library(testthat)
library(pillar)
library(clipr)
library(rmarkdown)
library(conflicted)
library(tidyr)
library(tidyverse)
library(dplyr)
conflict_prefer("filter", "dplyr")
conflict_prefer("mutate", "dplyr")
library(readxl)
library(here)
library(plyr)
conflict_prefer("summarize", "plyr")
conflict_prefer("summarise", "dplyr")
library(skimr)
library(kableExtra)
library(AMR)
library(scales)
library(pipeR)
library(cleaner)
library(htmlTable)
library(data.table)
library(janitor)
library(reshape)
library(reshape2)
conflict_prefer("melt", "reshape2")
library(summarytools)
conflict_prefer("freq", "cleaner")
library(magrittr)
library(epiDisplay)
conflict_prefer("select", "dplyr")
conflict_prefer("view", "tibble")
library(vcdExtra)
library(formattable)
library(gt)
conflict_prefer("chisq.test", "janitor")
setwd("E:/RESULTS/Mwaura/mwaura/WORK1/Covid19/Irene Work")
IRENE_DATA_ANALYSIS_R <- fread("IRENE DATA ANALYSIS R.csv")
```

### Summary of the data

View the summary of the data

```{r, echo=FALSE}
#skimr::skim(IRENE_DATA_ANALYSIS_R) %>% kbl(caption = "Summary") %>% kable_classic(full_width = F, html_font = "Cambria")
```
### Number of camels from each of the Livestock Production System 
With their Percentages and Bar Graph


```{r, echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% tabyl(Community,LPS) %>% adorn_totals(c("row","col")) %>%adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 0) %>%
  adorn_ns() %>%   kbl(caption = "Ranch vs Livestock production system With Percentages") %>% kable_classic(full_width = F, font = "Cambria") 


IRENE_DATA_ANALYSIS_R %>% select(Community,LPS) %>%  ggplot(aes(x=Community,fill=LPS))+geom_bar(color="black",fill="black")+ylab("Number of Camels")+stat_count(geom="text",aes(label=stat(count)), position = position_stack(vjust = .9),color="white")
```
### Counts and Percentages of E.coli Isolated from all the camels
This table counts and percentages of E.coli isolates in Extensive/Intensive location/Livestock procuction system

```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% tabyl(mo,LPS) %>%adorn_totals(c("col")) %>%  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 0) %>%
  adorn_ns() %>%  kbl(caption = "E.coli recovered from each of the LPS") %>% kable_classic(full_width = F,font = "Cambria")
```

###Pie Chart
The above table can be visualised as a pie chart
```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% select(mo,CAMEL_ID_NUMBER) %>% group_by(mo) %>%  dplyr::summarise(n = n()) %>% mutate(Percentage=paste0(round(n/sum(n)*100,0),"%")) %>% ggplot(aes(x="", y=mo, fill=Percentage)) + geom_bar(stat="identity", width=1)+ coord_polar("y" ,start=0) +theme_classic()+labs( title = "Percentage of E.coli  Detected")+scale_fill_manual(values=c( "black","grey"))+theme(axis.line = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(), plot.title = element_text(hjust = 0.5, color = "black"))+geom_text(aes(y = mo,label="E.coli"), position = position_stack(vjust = .5),color = "grey", size=6)

```
### Counts and percentages of the number of camels (female and male) from each livestock production system

```{r,echo=FALSE}
tab<-IRENE_DATA_ANALYSIS_R %>% tabyl(Gender,LPS)  
tab %>%  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 0) %>%
  adorn_ns()  %>% kbl(caption = "Camels(Female and Male) from each of the LPS") %>% kable_classic(full_width = F, font = "Cambria")
tab%>%chisq.test() 

```

### The count and percentages of  Resistance/Intermediate/Susceptible E.coli to all the antibiotics

```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% proportion_df(combine_SI = FALSE) %>% spread(key = interpretation,value = value) %>% adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 0)%>% kbl(caption = "Antibiotic Susceptability Intermediate and Resistance") %>%  kable_classic(full_width = F,font = "Cambria")
```


### Beta-lactams/penicillins
Beta-lactam antibiotics are one of the most commonly prescribed drug classes with numerous clinical indications.

From a biochemical point of view, these drugs have a common feature, which is the 3-carbon and 1-nitrogen ring (beta-lactam ring) that is highly reactive. This class includes:

Penicillins,Cephalosporins,Carbapenems,Monobactams,Beta-lactamase inhibitors

column 'AMC' (amoxicillin/clavulanic acid), column 'AMP'
                                    (ampicillin), column 'OXA' (oxacillin), column 'TEM' (temocillin)
NOTE: No antimicrobial agents of class cephalosporins (1st gen.) found (such as cefacetrile,
      cephapirin).
      Selecting cephalosporins (2nd gen.): column 'CEC' (cefaclor), column 'CXM' (cefuroxime)
NOTE: No antimicrobial agents of class carbapenems found (such as doripenem, imipenem).
```{r,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(AMP,AMP,CEC,FEP,CXM,CRO,CTX,CAZ)%>% mutate_at(vars(AMP:CAZ), as.rsi) %>% count_df(translate_ab = TRUE,combine_SI = FALSE) %>% spread(key =interpretation,value = value ) %>% adorn_percentages("row") %>%
    adorn_pct_formatting(digits = 0) %>%
    adorn_ns() %>%  kbl(caption = "
Beta-lactams/penicillins") %>%  kable_classic(full_width = F, font = "Cambria")
```
### Resisitance

```{r,echo=FALSE}

IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo)%>%filter(mo=="Escherichia coli") %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),SXT=resistance(SXT),NOR = resistance(NOR)) %>% tidyr::pivot_longer(-mo, names_to = "antibiotic") %>% ggplot(aes(x = mo,y = value,fill = antibiotic)) +geom_col(position = "dodge2")
```
### Comparison table(extensive and Intensive)-count and percentage , resistance to all antibiotics
```{r, echo=FALSE}
#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% proportion_df(combine_SI = FALSE) %>% spread(key = interpretation,value = value) %>% kbl(caption = "Antibiotic Susceptability Intermediate and Resistance") %>%  kable_classic(full_width = F, html_font = "Cambria")


#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,combine_SI = FALSE) %>% spread(key = antibiotic,value = value) %>% unnest()%>% kbl(caption = "Comparision of Livestock Production system with their resistant to all antibiotics") %>%  kable_classic(full_width = F, html_font = "Cambria")

#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,as_percent=FALSE,combine_SI = TRUE) %>% spread(key = antibiotic,value = value) %>% unnest()%>%  adorn_percentages("row") %>% adorn_pct_formatting(digits = 0)%>% kbl(caption = "Comparision of Livestock Production system with their resistant to all antibiotics") %>%  kable_classic(full_width = F, html_font = "Cambria")

anti<-IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,combine_SI = FALSE,as_percent = FALSE) %>% spread(key = antibiotic,value = value) %>% melt(id.vars=c("LPS","interpretation"),measure.vars=c("AMC","AMP","CAZ","CEC","CHL","CIP","CRO","CTX","CXM","FEP","GEN","NOR","SPT","SXT","TCY"))

#IRENE_DATA_ANALYSIS_R %>% select(LPS,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>%group_by(LPS) %>% proportion_df(translate_ab=FALSE,combine_SI = FALSE)  %>% spread(key = antibiotic,value = value) %>% melt(id.vars=c("LPS","interpretation"),measure.vars=c("AMC","AMP","CAZ","CEC","CHL","CIP","CRO","CTX","CXM","FEP","GEN","NOR","SPT","SXT","TCY")) %>% gt() %>% fmt_percent(columns = 4,decimals = 2)
anti1<-xtabs(value~LPS+interpretation+variable,data =anti )

structable(anti1) 


```
### Multdrug Resistance Organisms MDR

```{r,echo=FALSE}
#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro()%>% freq() %>%  kbl(caption = "Multdrug Resistance Organisms MDR") %>%  kable_classic(full_width = F, html_font = "Cambria")
IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro()%>% tab1( col=c("black","white"),cum.percent = FALSE) %>%  kbl(caption = "Multdrug Resistance Organisms MDR") %>%  kable_classic(full_width = F, font = "Cambria")

```

### Antibiotic Profiling

```{r, echo=FALSE,error= FALSE,cache=FALSE}
#par(mar=rep(2,4))
#IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(ISOLATE_ID,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi)
#IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(ISOLATE_ID,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi) %>% melt(id="ISOLATE_ID") %>% filter(value=="R") 

prof<-IRENE_DATA_ANALYSIS_R %>%filter(mo=="Escherichia coli") %>%  select(ISOLATE_ID,AMC:NOR)%>% mutate_at(vars(AMC:NOR), as.rsi) %>% melt(id="ISOLATE_ID") %>% filter(value=="R") 

Profile<-plyr:: ddply(prof, .(ISOLATE_ID), summarize,  antibiotics=paste(variable,collapse=",")) 

Profile2<-tab1(Profile$antibiotics, sort.group = "decreasing",col=c("black","white"), cum.percent = FALSE,main ="Profile of antibiotics",cex.names = 0.7,cex=0.5,,cex.main=1,cex.axis=0.7,cex.lab=0.7 )
Profile2 %>% kbl(caption = "Profile of antibiotics") %>% kable_classic(full_width = F, font = "Cambria")

#prof2<-prof1 %>% summarytools::freq(prof1$antibiotics,order = "freq",cumul=FALSE,report.nas = FALSE)