---
title: "MDRO"
author: "Mwaura Patrick"
date: "1/27/2021"
output:
  html_document: default
  word_document: default
---

title: "Irene Data analysis"
author: "Mwaura Patrick"
date: "1/27/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r load relevant librararies,echo=FALSE, message=FALSE,warning=FALSE}
options( warn = -1 )
library(tidyverse)
library(dplyr)
library(readxl)
library(here)
library(skimr)
library(kableExtra)
library(AMR)
library(scales)
library(pipeR)
library(cleaner)
library(htmlTable)
library(data.table)
library(janitor)
```

# Set the working directory and load the data

```{r read file ,echo=FALSE}
setwd("E:/RESULTS/Mwaura/mwaura/WORK1/Covid19/Irene Work")
IRENE_DATA_ANALYSIS_R <- read_csv("IRENE DATA ANALYSIS R.csv")
```

# Explore the data

```{r view the data frame,echo=FALSE}
#skimr::skim(IRENE_DATA_ANALYSIS_R)
```
# Brief summary
```{r summaries of Micro-organisms,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% select(mo,CAMEL_ID_NUMBER) %>% group_by(mo) %>%  summarize(Count=n()) %>% mutate(Percentage=paste0(round(Count/sum(Count)*100,2),"%")) %>% kbl(caption = "Proportion of Each Categories of Organisms") %>% kable_classic(full_width = F, html_font = "Cambria")

#IRENE_DATA_ANALYSIS_R %>% freq(mo) %>%
 # kbl(caption = "Proportion of Each Categories of Organisms") %>%
 # kable_classic(full_width = F, html_font = "Cambria")

#IRENE_DATA_ANALYSIS_R %>% select( ISOLATE_ID, Gender,mo) %>% pivot_wider(names_from = mo, values_from=ISOLATE_ID,values_fn=list(ISOLATE_ID=list))

IRENE_DATA_ANALYSIS_R %>% tabyl(Gender,mo) %>%adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>%  kbl(caption = "Gender vs Organisms With Percentages") %>% kable_classic(full_width = F, html_font = "Cambria")
```


```{r summaries of Micro-organisms,echo=FALSE}
IRENE_DATA_ANALYSIS_R %>% select(mo,CAMEL_ID_NUMBER) %>% group_by(mo) %>%  summarize(Count=n()) %>% mutate(Percentage=paste0(round(Count/sum(Count)*100,2),"%")) %>% ggplot(aes(x="", y=mo, fill=Percentage)) + geom_bar(stat="identity", width=1)+ coord_polar("y", start=0) +theme_classic()+labs( title = "Percentage of Particular Organism Detected")+scale_fill_manual(values=c("#55DDE0", "#33658A", "#2F4858", "#F6AE2D"))+theme(axis.line = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(), plot.title = element_text(hjust = 0.5, color = "#666666"))+geom_text(aes(y = mo, label = mo), position = position_stack(vjust = .5),color = "white", size=3)
```


```{r summaries of Micro-organisms,echo=FALSE}
```
# Cross tabulation by Ranch_community vs the livestock production system
LPS-lIVESTOCK PRODUCTION SYSTEM
```{r   Ranch or community representation of the production system, echo=FALSE}
#IRENE_DATA_ANALYSIS_R %>% select(  Community,LPS) %>% pivot_wider(names_from = LPS, values_from= LPS,values_fn=list(LPS=list))
IRENE_DATA_ANALYSIS_R %>% tabyl(Community,LPS) %>%adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_ns() %>%  kbl(caption = "Ranch va Livestock production system With Percentages") %>% kable_classic(full_width = F, html_font = "Cambria")

#IRENE_DATA_ANALYSIS_R %>% select( ISOLATE_ID, Community,LPS) %>% group_by(ISOLATE_ID,Community)

IRENE_DATA_ANALYSIS_R %>% select(Community,LPS) %>%  ggplot(aes(x=Community,fill=LPS))+geom_bar()+ylab("Count of Camels")+stat_count(geom="text",aes(label=stat(count)), position = position_stack(vjust = .5),color="black")
```
# MDRO analysis
```{r Mult_drug Resistant Organisms ,echo=FALSE,message=FALSE,warning=FALSE}
IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi)%>% mdro()%>% freq() %>% kbl(caption = "MDR") %>%
  kable_classic(full_width = F, html_font = "Cambria")


```
# Resistance
Amoxicillin/clavulanic acid	AMC
Ampicillin 	AMP.Ceftazidime	CAZ.Cefotaxime	CTX.Ceftriaxone	CRO.Cefuroxime	CXM.Cefepime	FEP.Cefaclor	CEC.Tetracycline	TCY.Gentamicin	GEN.Spectinomycin	SPT.Chloramphenicol	CHL.Ciprofloxacin	CIP.Trimethoprim/sulfamethoxazole	SXT.Norfloxacin	NOR

```{r Resistance of e.coli to various antibitics,echo=FALSE,warning=FALSE}
IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo) %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),SXT=resistance(SXT),NOR = resistance(NOR))%>% kbl(caption = "MDR") %>%
  kable_classic(full_width = F, html_font = "Cambria",font_size =9)

IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo) %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),SXT=resistance(SXT),NOR = resistance(NOR)) %>% tidyr::pivot_longer(-mo, names_to = "antibiotic") %>% ggplot(aes(x = mo,y = value,fill = antibiotic)) +geom_col(position = "dodge2")


#IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo) %>% summarise(AMC= resistance(AMC), AMP = resistance(AMP),CAZ=resistance(CAZ),CTX=resistance(CTX),CRO=resistance(CRO),CXM=resistance(CXM),FEP=resistance(FEP),CEC=resistance(CEC),TCY=resistance(TCY),GEN=resistance(GEN),SPT=resistance(SPT),CHL=resistance(CHL),CIP=resistance(CIP),TrSXT=resistance(SXT),NOR = resistance(NOR)) %>% tidyr::pivot_longer(-mo, names_to = "antibiotic") %>%ggplot(mapping = aes(x = mo,y = value)) +geom_col() +labs(title = "Micro-organisms",subtitle = "Resistance to Antibiotics", x = "Organism",y = "Resistance Rates")

```
# Conduct principal component analysis (PCA) for AMR
```{r, echo=FALSE}
options(warn = -1)
#IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo) %>% count_df(combine_SI = FALSE) %>% kbl(caption = "Antibiotic Susceptability and Resistance") %>%  kable_classic(full_width = F, html_font = "Cambria") 

IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% proportion_df(combine_SI = FALSE) %>% spread(key = interpretation,value = value) %>% kbl(caption = "Antibiotic Susceptability Intermediate and Resistance") %>%  kable_classic(full_width = F, html_font = "Cambria")


#profile<-IRENE_DATA_ANALYSIS_R %>% filter(mo=="Escherichia coli") %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo) %>% count_df(combine_SI = FALSE)

#profile %>%group_by(antibiotic) %>% spread(interpratation,value) %>% kbl(caption = "Antibiotic Susceptability and Resistance") %>%  kable_classic(full_width = F, html_font = "Cambria") 
     #resistance_data<-IRENE_DATA_ANALYSIS_R %>% select(mo,AMC:NOR) %>% mutate_at(vars(AMC:NOR), as.rsi) %>% group_by(mo) %>% summarise_if(is.rsi, resistance) %>% select(mo,AMC:NOR)

#resistance_data %>%kbl(caption = "MDR") %>%
#  kable_classic(full_width = F, html_font = "Cambria",font_size =9)


#resistant_data_2<-data.frame(na.omit(resistance_data))

#resistant_data_2%>% kbl(caption = "MDR") %>%
#(full_width = F, html_font = "Cambria",font_size =9 )
```

